Models

### 2023-03-21 Code/Models.Rmd
Updated rank sum test

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(Time, cluster = Athlete, data = comp, paired = TRUE, alternative = "greater", method = "rgl")
#pairwise.clusWilcox.test(comp$Time, group= comp$Year, cluster = comp$Athlete, alternative = "greater", method = "rgl")
```

@@

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, paired = TRUE, alternative = "greater", method = "rgl")
```

@@

>>>>

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp, alternative = "greater", method = "ds")
#clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp, alternative = "greater", method = "rgl")
#pairwise.clusWilcox.test(comp$Time, group= comp$Year, cluster = comp$Athlete, alternative = "greater", method = "rgl")
```

@@

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, alternative = "greater", method = "ds")
#clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, paired = TRUE, alternative = "greater", method = "rgl")

```

@@

```{r}
library(xtable)
xtable(men_pooled_year_gamma_log)
```
```{r}
library(memisc)
mtable(men_pooled_year_gamma_log)
```
